\documentclass[../main.tex]{subfiles}
\begin{document}
\begin{song}[3]{Bohemian Rhapsody}{Queen}{}
[Em7]Is this the real life, [A7]is this just fantasy?
[D7]Caught in a [Am7]landsl[D7]ide, no e[G]scape from reality
[Em]Open your eyes, look [G7]up to the skies and s[C]ee
[Am]I'm just a poor boy, [D7]I need no sympathy
Because I'm [G#]easy [G]come, [F#]easy [G]go, [G#]little [G]high, [F#]little [G]low,
[C]Any way the [G]wind blows, [A#dim7]doesn't really [D7]matter to me, to [G]me

[G]Mama, just [Em]killed a man,
Put a [Am]gun against his head, pulled my trigger, now he's d[D]ead,
[G]Mama, life had [Em]just begun,
But [Am]now I've gone and thrown it all away
[C]Mama [G]oo[Am]ooh, didn't [Dm]mean to make you cry
If [G]I'm not back again this time tom[C]orrow
Carry [G]on, carry [Am]on, as if [Fm]nothing really mat[C]ters[G]{\h}

[G]Too late, my [Em]time has come,
Sends [Am]shivers down my spine, body's aching all the ti[D]me,
[G]Goodbye everybody - I've [Em]got to go
Gotta [Am]leave you all behind and face the truth
[C]Mama [G]oo[Am]ooh, [Dm]I don't want to die,
I [G]sometimes wish I'd never been born at a[C]ll


I see a little silhouetto of a man,
Scaramouche, scaramouche, will you do the Fandango
Thunderbolt and lightning, very very frightening me
Galileo, Galileo, Galileo, Galileo, Galileo, Figaro Magnifico
I'm just a poor boy, no-body loves me.
He's just a poor boy from a poor family.
Spare him his life from this monstrosity.
Easy come, easy go, will you let me go?  Bismillah!
No, we will not let you go. Let him go! Bismillah!
We will not let you go. Let him go! Bismillah!  We will not let you go. Let me go!
Will not let you go. Let me go! Will not let you go. Let me go! Ahhhhhhhhh
No, no, no, no, no, no, no.  Oh, mama mia, mama mia
Mama mia, let me go. Beelzebub has a devil put aside for me

[G]So you think you can stone me and [C]spit in my [G]eye[A#]{\h}
[G]So you think you can love me and [C]leave me to [F]die
[Dm]Oh, [G]baby -[Dm] can't do this to me, [G]baby
[Dm]Just gotta get [G]out - [Dm]just gotta get [G]right outta [C]here

[Am]Nothing really mat[Em]ters,
[Am]Anyone can [Em]see,
[Am]Nothing really mat[Fm]ters, [F]nothing really matters to [C]me,

[G]Any [D]way the [Ddim]wind [Em7]blows .[D]..
\end{song}
\end{document}