\documentclass[../main.tex]{subfiles}
\begin{document}
\begin{song}[4]{Four Chords}{The Axis of Awesome}{}
[C]My life is brilliant, [G]my love is pure, 
[Am]I saw an angel, [F]of that I'm sure
[C]People killing people dy[G]ing, children hurtin you hear them cr[Am]ying
Can you practice what you pr[F]each? Would you turn the other cheek?
[C]Forever yo[G]ung, [Am]I wanna be forever you[F]ng
[C]I won't hesitate no more, n[G]o more, 
[Am]it cannot wait, [F]I'm Yours
[C]Your lipstick stains [G]on the front lobe of my left side brains
[Am]I knew I wouldn't [F]forget you. 
[C]If I could, [G]then I would, [Am]I'll go wherev[F]er you will go

[C]And can [G]you feel [Am]the love [F]tonight
[C]Nobody wants to see us[G] together, [Am]but it d[F]on't matter no\h \sprache{'cause I got you}
Country r[C]oads, take me h[G]ome to the p[Am]lace I belo[F]ng
I'[C]m your biggest fan, I[G]'ll follow you until you lo[Am]ve me, Papa-[F]Paparazzi
I can't l[C]ive[G] with or witho[Am]ut you[F]{\h}
Pictures of y[C]ou, pictures of m[G]e, hung upon your wa[Am]ll for the world to se[F]e
And she wi[C]ll be love[G]d. she wi[Am]ll be love[F]d

When I f[C]ind myself in ti[G]mes of trouble, [Am]Mother Mary co[F]mes to me
[C]No, w[G]oman, no c[Am]ry[F]{\hh}
Yeah, Mama this s[F]urely is a dr[C]eam
I come from a [G]land down under[Am]{\hh}[F]{\hh}

[C]Red, white and bl[G]ue all the [Am]funny things you d[F]o, [C]America, Americ[G]a, This is y[Am]ou[F]{\hh}
[C]Take [G]on [Am]me - [F]When I come around - [C]Take [G]me [Am]on - [F]When I come around

[C]I'll [G]be [Am]gone, [F]when I'm on take
[Am]Its gonna take a lot[F] to drag me away from you
Theres nothing that a hu[F]ndred men or m[C]ore could ever [G]do

I'm to[C]rn into piec[G]es, can't de[Am]ny it, can't pre[F]tend
Just tho[C]ught you were the o[G]ne, in my he[Am]ad I s[F]ee y[C]ou all over [G]me.
In my h[Am]ead, y[F]ou fulf[C]ill [G]my fantasy, in my head
[Am]Despite all [F]my ra[C]ge I a[G]m still just a rat in a cage
[Am]What [F]if God[G] was one[C] of us
[Am]I Kn[F]ow she'[C]s playin with [G]me, [Am]well thats o[F]k coz I [C]got no self [G]esteem
[Am]With a [F]1,000 eyes and a [C]great [G]disguise I'll l[Am]ook em right[F] between the [C]eyes
hit them [G]right between the eyes
\pagebreak
'cause you're so be[Am]autiful[F], so damn beau[C]tiful[G]{\h}
It's too l[Am]ate to apologi[F]ze, too la[C]te[G]
Just gonna st[Am]and there and watch me b[F]urn
But that's al[C]right because I like the way it h[G]urts
It's my li[Am]fe, it's no[F]w or never
[C]I ain't gonna li[G]ve forever
[Am]Can't read my, can't read m[F]y, no he can't read my p[C]oker face
C[G]ome on Barbie, let's go party!

[N.C.]And doesn't that sound fami[C]liar?
Doesn't that hit too cl[G]ose to home?
Doesn't that make you sh[Am]iver?
The way things could have go[F]ne.
And doesn't it feel pec[C]uliar,
When everyone wants a l[G]ittle more?
So that I do rem[Am]ember to never go this f[F]ar
That's all it takes to be a st[C]ar

\end{song}
\end{document}