\documentclass[../main.tex]{subfiles}
\begin{document}
\begin{song}[2]{Hey There Delilah}{Plain White T's}{}
[C]{}\hh[Em]{\h}[C]{\h}[Em]{\h}
[C]Hey there Delilah, What’s it [Em]like in New York City?
I’m a [C]thousand miles away, But girl to[Em]night you look so pretty,
Yes you [Am]do, [F]Time Square can’t [G]shine as bright as [Am]you, I swear it’s [G]true.

[C]Hey there Delilah, Don’t you [Em]worry about the distance,
I’m right [C]there if you get lonely, Give this [Em]song another listen,
Close your [Am]eyes, [F]Listen to my [G]voice it’s my dis[Am]guise, I’m by your [G]side.

\gSec{Chorus}
[C]Oh it’s what you do to [Am]me, [C]Oh it’s what you do to [Am]me,[G]{\h}
[C]Oh it’s what you do to [Am]me, [C]Oh it’s what you do to [Am]me, What you do to [C]me.

[C]Hey there Delilah, I know [Em]times are getting hard,
But just be[C]lieve me girl some day, I'll pay the [Em]bills with this guitar,
We'll have it [Am]good, [F]We'll have the [G]life we knew we [Am]would, My word is [G]good.

[C]Hey there Delilah, I’ve got [Em]so much left to say,
If every [C]simple song I wrote to you, Would [Em]take your breath away,
I’d write it [Am]all, [F]Even more in [G]love with me you’d [Am]fall, We’d have it [G]all.

\gSec{Chorus}
[C]Oh it’s what you do to [Am]me, [C]Oh it’s what you do to [Am]me,[G]{\h}
[C]Oh it’s what you do to [Am]me, [C]Oh it’s what you do to [Am]me,[G]{\h}

[F]A thousand miles seems pretty far, But [G]they’ve got planes and trains and cars,
[C]I’d walk to you if I had no other [Am]way
[F]Our friends would all make fun of us, And [G]we'll just laugh along because,
We [C]know that none of them have felt this [Am]way,
[F]Delilah I can promise you, That [G]by the time that we get through,
The [Am]world will never ever be the same, And you’re to [G]blame.

[C]Hey there Delilah you be [Em]good, And don’t you miss me,
Two more [C]years and you’ll be done with school, And [Em]I'll be making history,
Like I [Am]do, [F]You’ll know it's [G]all because of [Am]you,
[F]We can do what[G]ever we want [Am]to,
[F]Hey there De[G]lilah here's to [Am]you, This one’s for [G]you.

\gSec{Chorus}
[C]Oh it’s what you do to [Am]me, [C]Oh it’s what you do to [Am]me,[G]{\h}
[C]Oh it’s what you do to [Am]me, [C]Oh it’s what you do to [Am]me, what you do to [C]me.
Ohh[Am]h\hh[C]{\h}[Am]{\h}[C]{\h}[Am]{\h}[C]{\h}[Am]{\h}[C]{\h}[C]{\h}

\end{song}
\end{document}