\documentclass[../main.tex]{subfiles}
\begin{document}
\begin{song}[7]{Home}{Edward Sharpe and the Magnetic Zeros}{}
[Em]Alabama, Arkansas, [G]I do love my ma and pa,
[G/B]Not the way that[G] I do love[C] you. \hh\sprache{Home!}

[Em]Well, Holy, Moley, me, oh my, [G]you're the apple of my eye,
[G/B]Girl I've never [G]loved one like[C] you. \hh\sprache{Home!}

[Em]Man oh man you're my best friend, [G]I scream it to the nothingness,
[G/B]There ain't[G] nothing that I[C] need. \hh\sprache{Home!}

[Em]Well, hot and heavy, pumpkin pie, [G]Chocolate candy, Jesus Christ,
[G/B]Ain't nothing[G] please me more than[C] you.

\gSec{Refrain}
Ahh [Em]Home. Let me come [G]home
[G/B]Home is whe[G]rever I'm with[C] you.
Ahh [Em]Home. Let me go ho[G]-oh-ome.
[G/B]Home is whe[G]rever I'm with[C] you.

[Em]I'll follow you into the park, [G]Through the jungle through the dark,
[G/B]Girl I never[G] loved one like[C] you. \hh\sprache{Home!}

[Em]Moats and boats and waterfalls, [G]Alley-ways and pay phone calls,
[G/B]I've been[G] everywhere with[C] you. \hh\sprache{Home!}

[Em]We laugh until we think we’ll die, [G]barefoot on a summer night
[G/B]Never could be[G] sweeter than with[C] you \hh\sprache{Home!}

[Em]And in the streets you run afree, [G]like it's only you and me,
[G/B]Geeze, you're[G] something to[C] see.

\gSec{Refrain}
Ahh [Em]Home. Let me come [G]home
[G/B]Home is whe[G]rever I'm with[C] you.
Ahh [Em]Home. Let me com[G]e ho-oh-ome.
[G/B]Home is whe[G]rever I'm with[C] you.

[Em]Home. Let me come [G]home.
[NC.]Home is wherever I'm with [C]you.

[Em]Ahh home. Yes I am [G]ho-oh-ome. Home is when I'm alone with [C]you.
[Em]Alabama, Arkansa[G]s, [G/B]I do love my[G] ma and[C] pa...
[Em]Moats and boats and water[G]falls, [G/B]Alley-ways and[G] pay phone[C] calls...

[G/B]Home is when[G] I'm alone with[C] you.
[G/B]Home is when[G] I'm alone with[C] you...
\end{song}
\end{document}