\documentclass[../main.tex]{subfiles}
\begin{document}
\begin{song}{Losing My Religion}{R.E.M.}{}
Oh, [Am]life is bigger,[Em]{\hh}
It's bigger than you and you are [Am]not me.
The lengths that I will [Em]go to, the distance in your [Am]eyes,[Em]{\hh}
Oh no, I've said too [Dm]much, I set it [G]up.

\gSec{Chorus}
That's me in the [Am]corner, 
That's me in the [Em]spotlight, losing my re[Am]ligion.
Trying to [Em]keep up with you. And I [Am]don't know if I can do it.[Em]{\hh}
Oh no, I've said too [Dm]much, I haven't said e[G]nough.

I [G]thought that I heard you [F]laughing, I [Dm]thought that I [G]heard you [Am]sing.
[Am]I th[F]ink I thought I [Dm]saw [G]you [Am]try.[G]{\hh}

Every whis[Am]per of every waking h[Em]our, I'm choosing my con[Am]fessions,
Trying to [Em]keep an eye on you, like a [Am]hurt lost and blinded fool, fool[Em]{\hh}
Oh no, I've said too [Dm]much, I set it [G]up.

Consider [Am]this, consider this, the [Em]hint of a century,
Consider [Am]this: the slip that [Em]brought me to my knees failed.
[Am]What if all these fantasies come [Em] flailing around?
Now I've [Dm]said too [G]much.

I th[G]ought that I heard you l[F]aughing, I though[Dm]t that I h[G]eard you s[Am]ing.
[Am]I  th[F]ink I thought I [Dm]saw [G]you [Am]try.[G]{\hh}

But [C]that was just a [Dm]dream, [C]that was just a [Dm]dream.

\gSec{Chorus}
That's me in the [Am]corner, 
That's me in the [Em]spotlight, losing my re[Am]ligion.
Trying to [Em]keep up with you. And I [Am]don't know if I can do it.[Em]{\hh}
Oh no, I've said too [Dm]much, I haven't said e[G]nough.

I th[G]ought that I heard you la[F]ughing, I [Dm]thought that I [G]heard you [Am]sing.
[Am]I  [F]think I thought I s[Dm]aw y[G]ou t[Am]ry.
But [F]that was just a [Dm]dream[G],
[Am]Try, cry, why, try.
[F]That was just a dream,[Dm] j[G]ust a d[Am]ream, just a d[G]ream, dream.
\end{song}
\end{document}