\documentclass[../main.tex]{subfiles}
\begin{document}
\begin{song}[6]{Sound of Silence}{Simon and Garfunkel}{}
[Am]Hello darkness, my old [G]friend,
I've come to talk with you [Am]again,
Because a vision soft[F]ly creep[C]ing,
Left its seeds while I [F]was slee[C]ping,
And the [F]vision that was planted in my [C]brain
Still remains[Am]{\hh}

[C]Within the s[G]ound of s[Am]ilence.
In restless dreams I wal[G]ked alone
Narrow streets of cobble[Am]stone,
'neath the halo of [F]a street [C]lamp,
I turned my collar to the [F]cold and [C]damp
When my [F]eyes were stabbed by the flash of a neon [C]light
That split the night[C]{\hh}[Am]{\hh}
A[C]nd touched the [G]sound of [Am]silence.

And in the naked light I [G]saw
Ten thousand people, maybe [Am]more.
People talking with[F]out spea[C]king,
People hearing with[F]out liste[C]ning,
People writing [F]songs that voices never [C]share
And no one dar[C]e[Am]
[C]Disturb the [G]sound of [Am]silence.

Fools said I, you do not [G]know
Silence like a cancer [Am]grows.
Hear my words that I [F]might teach [C]you,
Take my arms that I [F]might reach [C]you.
But my [F]words like silent raindrops [C]fell,[Am]
And[C] echoed
In the [G]wells of [Am]silence

And the people bowed and [G]prayed
To the neon God they [Am]made.
And the sign flashed out [F]its war[C]ning,
In the words that it w[F]as for[C]ming.
And the sign said, the [F]words of the prophets
Are written on the subway w[C]alls
And tenement [C]halls.[Am]
And whisp[C]er'd in the [G]sounds of [Am]silence.
\end{song}
\end{document}