\documentclass[../main.tex]{subfiles}
\begin{document}
\begin{song}{Sweet Home Alabama}{Lynyrd Skynyrd}{}\gSec{Intro $\times$4}\begin{tabline}{1}{6}{8}{E,A,D,G,B,E}
		\notewithchord{1}{11}{4}{0}{D}
		\note{2}{11}{4}{0}
		\note{3}{11}{2}{3}
		\note{4}{11}{3}{2}
		\notewithchord{5}{11}{5}{3}{C}
		\note{6}{11}{5}{3}
		\note{7}{11}{2}{0}
		\note{8}{11}{3}{3}
		\notewithchord{9}{11}{6}{3}{G}
		\note{10}{11}{6}{3}
		\note{11}{11}{1}{3}
		\note{11}{11}{2}{3}
		\note{11}{11}{3}{0}
		\note{11}{11}{4}{0}
		\note{11}{11}{5}{2}
		\note{11}{11}{6}{3}
		\nextbar
\end{tabline}

[D]Big [C]wheels keep on [G]turning
[D]Carry me [C]home to see my [G]kin.
[D]Singing [C]songs about the [G]southland
[D]I miss'ole' '[C]bamy once a[G]gain (and I think it's a sin)


[D] \hh[C] \hh[G] \hh[D] \hh[C] \hh[G] \hh

[D]Well, I heard Mister [C]Young sing a[G]bout her
[D]Well, I heard ole [C]Neil put her [G]down.
[D]Well, I hope Neil [C]Young will re[G]member,
[D]A southern [C]man don't need him a[G]round anyhow

\gSec{Chorus}
[D]Sweet [C]home Ala[G]bama, [D]where the [C]skies are so [G]blue,
[D]Sweet [C]home Ala[G]bama, [D]Lord, I'm [C]coming home to [G]you.


[D] \hh[C] \hh[G] \hh[D] \hh[C] \hh[G] \hh

[D]In Birmingham they [C]love the [G]Gov'nor   [F]Boo  [C]hoo  [D]hoo !
[D]Now we all [C]did what we could [G]do.
[D]Now Watergate [C]does not bother [G]me.
[D]Does your [C]conscience bother [G]you?  (tell the truth)

\gSec{Chorus}
[D]Sweet [C]home Ala[G]bama,
[D]Where the [C]skies are so [G]blue,
[D]Sweet [C]home Ala[G]bama,
[D]Lord, I'm [C]coming home to [G]you.


[D] \hh[C] \hh[G] \hh[D] \hh[C] \hh[G] \hh

[D]Now Muscle [C]Shoals has got the [G]Swampers
[D]And they've been [C]known to pick a [G]tune or two
[D]Lord they [C]get me off so [G]much
[D]They pick me [C]up when I'm feeling [G]blue (Now how about you?)

\gSec{Chorus $\times$2}
[D]Sweet [C]home Ala[G]bama, [D]where the [C]skies are so [G]blue,
[D]Sweet [C]home Ala[G]bama, [D]Lord, I'm [C]coming home to [G]you.


[D] \hh[C] \hh[G] \hh[D] \hh[C] \hh[G] \hh
\end{song}
\end{document}